Probabilistic Programming around Gaussian Processes

### 2019-10-19 abstract/paper.tex
abstract in progress

\acmConference[LAFI'2019]{Languages for Inference}{January 15,
2019}{Lisbon, Portugal}

@@

\title{Server-Side Probabilistic Programming}
\author{David Tolpin}
\affiliation{
    \institution{PUB+}
    \country{Israel}
}
\email{david.tolpin@gmail.com}

\begin{abstract}
	We share our experiences from integrating probabilistic
	programming into a server-side software system and
	present our ongoing work on probabilistic programming
	facility for Go, a modern programming language of choice for
	server-side software development. We demonstrate how a
	lightweight efficient probabilistic programming facility can
	be added to an existing programming language.  Server-side
	application of probabilistic programming poses challenges
	for a probabilistic programming system. We discuss the
	challenges and our experience in overcoming them, and
	suggest guidelines that can help in a wider adoption of
	probabilistic programming in server-side software systems.
\end{abstract}

@@

\begin{sloppypar}
\section{Challenges of Server-Side Probabilistic Programming}

>>>>

\acmConference[LAFI'2020]{Languages for Inference}{January 21,
2020}{New Orleans, LA, USA}

@@

\title{Probabilistic Programming around Gaussian Processes}
\author{David Tolpin}
\affiliation{
    \institution{PUB+}
    \country{Israel}
}
\email{david.tolpin@gmail.com}

\begin{abstract}
	We present GoGP, a library for probabilistic programming around
	Gaussian processes. Kernels, beliefs about hyperparameters
	and about observation inputs and outputs are
	programmatically expressed using the same differentiable
	probabilistic programming framework. One one hand, a basic
	usage with maximum-likelihood hyperparameter estimates and
	homoscedastic Gaussian noise requires as little coding as
	with any Gaussian process library. On the other hand,
	imposing prior beliefs on hyperparameters, handling input
	uncertainty, heteroscedastic and non-Gaussian noise, or
	change point detection can be organically added on top of a
	Gaussian process kernel. Just like distributions in
	probabilistic programs, kernels can be flexibly combined
	using general code flow rather than through predefined
	combination operators (usually addition and multiplication).
	Implemented in Go, a general-purpose programming language 
	popular for server-side programming, our library is well
	suited for integration into data processing/machine learning
	pipelines.  We demonstrate different uses of the library on
	a variety of case studies inspired by applications.
\end{abstract}

@@

\begin{sloppypar}
	\section{Gaussian Processes in Applications}

	Gaussian processes~\cite{} possess properties that make
	them the approach of choice in many applications:
	\begin{itemize}
		\item A Gaussian process works with as little or as much
			data as available.
		\item Non-uniformly sampled observations, missing
			observations, and observation noise are handled
			organically.
		\item Libraries for inference with Gaussian processes
			are readily available, both standalone and within
			ubiquitous machine learning libraries, such that
			Gaussian processes can be included into data
			processing pipelines and combined with other machine
			learning algorithms.
	\end{itemize}

\section{Challenges of Server-Side Probabilistic Programming}
